An Analysis of the Feasibility and Performance of BitTorrent as a Data Transfer Protocol in Peer to Peer Backup Systems

### 2014-04-30 paper/paper.tex
Paper: Add coloring to the system design figure and a sentence describing the coloring.
Paper: Add "recovery" to abstract

\begin{abstract}
For many computer users, having access to a reliable file backup service is important. As computers and computer-related technologies improve, users have the ability to generate higher resolution content. Creating backups becomes less feasible as the amount of data grows; limited network bandwidth makes the backup process cumbersome, and access to a large amount of storage space for backups is either limited or expensive. In this report, we propose a new backup system, BTBackup, which aims to solve both problems. Our system is designed as a Peer-to-Peer (P2P) network, where users of the system use each other as backup locations. Users offer storage space that is proportional to the amount of data that they back up. This means that the capacity of each user's physical storage is the only limiting factor for how much they can back up. We solve the problem of long data transfers for big files by leveraging the speed offered by the BitTorrent Protocol, which uses a file chunking mechanism to download files from multiple peers at once. By testing our system in various scenarios, we show that it achieves our goal of quicker backup creation through the use of file transfer parallelization.
\end{abstract}

@@

As mentioned in Section \ref{sec:EffectsofChurn_chap:Results}, our system could see much lower replication rates if the average uptime per peer is longer. In order to help increase the average, the fairness mechanism described in Section \ref{sec:Fairness_chap:BTBackup} could be extended to offer an incentive for having high uptimes. When a peer stays online for a long time, it could be awarded more space to backup data. This could increase the likelihood that users keep their machines online for longer periods of time, since it essentialy gives them free storage. However, if a system like this were to be implemented, there are several problems that need to be addressed. If some users are getting more storage space than what they are offering, then other users would be getting less space than what they are offering. Our system would not only need to determine who gets less storage space, but also what to do if many users are staying online often; it is possible that most people do this, so there is not much extra storage space to offer. In addition to this, we would need to figure out when to revoke extra space, in case malicious nodes attempt to game the system and limit their availability after being awarded space. If this is the case, more decisions need to be made in order to determine which replicas will be removed from the system, if the peer is using some or all of the space that is being revoked.

>>>>

\begin{abstract}
For many computer users, having access to a reliable file backup service is important. As computers and computer-related technologies improve, users have the ability to generate higher resolution content. Creating backups becomes less feasible as the amount of data grows; limited network bandwidth makes the backup process cumbersome, and access to a large amount of storage space for backups is either limited or expensive. In this report, we propose a new backup system, BTBackup, which aims to solve both problems. Our system is designed as a Peer-to-Peer (P2P) network, where users of the system use each other as backup locations. Users offer storage space that is proportional to the amount of data that they back up. This means that the capacity of each user's physical storage is the only limiting factor for how much they can back up. We solve the problem of long data transfers for big files by leveraging the speed offered by the BitTorrent Protocol, which uses a file chunking mechanism to download files from multiple peers at once. By testing our system in various scenarios, we show that it achieves our goal of quicker backup creation and recovery through the use of file transfer parallelization.
\end{abstract}

@@

As mentioned in Section \ref{sec:EffectsofChurn_chap:Results}, our system could see much lower replication rates if the average uptime per peer is longer. In order to help increase the average, the fairness mechanism described in Section \ref{sec:Fairness_chap:BTBackup} could be extended to offer an incentive for having high uptimes. When a peer stays online for a long time, it could be awarded more space to backup data. This could increase the likelihood that users keep their machines online for longer periods of time, since it essentially gives them free storage. However, if a system like this were to be implemented, there are several problems that need to be addressed. If some users are getting more storage space than what they are offering, then other users would be getting less space than what they are offering. Our system would not only need to determine who gets less storage space, but also what to do if many users are staying online often; it is possible that most people do this, so there is not much extra storage space to offer. In addition to this, we would need to figure out when to revoke extra space, in case malicious nodes attempt to game the system and limit their availability after being awarded space. If this is the case, more decisions need to be made in order to determine which replicas will be removed from the system, if the peer is using some or all of the space that is being revoked.
